Vector quantisation and partitioning of COVID-19 temporal dynamics in the United States

### 2020-08-02 paper/paper.tex
Final pre-submission proof.

Time series clustering presents a particular complication of this problem insofar as the subject of clustering is not a vector representing a single value, but rather a time series. These time series are typically not in synchrony, but rather exhibit a range of delays, lags and leads, and may depend on extrinsic and/or hidden variables. We may formulate the essential task of time series clustering as follows. Let $\mathcal{T}$ be a set of $n$ time series $x_{1 \ldots t_{max}}$. Further, let $k$ denote the cardinality of the label set $\mathcal{L}$ -- in other words, the number of partitions we wish to split the data into, with $k \leq n$. Then, the mapping $f: \mathcal{T} \rightarrow l \ | \ l \in \mathcal{L}$ is a clustering of the set of time series if it assigns to any element $x_i \in X \ | \ i \leq n$ one (and only one) label $l_i \in \mathcal{L}$, so as to minimise an objective function (typically referred to in this context as a distance metric) $J$ within each cluster $C_j = {x_p \in \mathcal{T} | l_p = j, j \in \mathcal{L}}$ defined by its label.

>>>>

Time series clustering presents a particular complication of this problem insofar as the subject of clustering is not a vector representing a single value, but rather a time series. These time series are typically not in synchrony, but rather exhibit a range of delays, lags and leads, and may depend on extrinsic and/or hidden variables. We may formulate the essential task of time series clustering as follows. Let $\mathcal{T}$ be a set of $n$ time series $x_{1 \ldots t_{max}}$. Further, let $k$ denote the cardinality of the label set $\mathcal{L}$ -- in other words, the number of partitions we wish to split the data into, with $k \leq n$. Then, the mapping $f: \mathcal{T} \rightarrow l \ | \ l \in \mathcal{L}$ is a clustering of the set of time series if it assigns to any element $x_i \in X \ | \ i \leq n$ one (and only one) label $l_i \in \mathcal{L}$, so as to minimise an objective function (typically referred to in this context as a distance metric) $J$ within each cluster $C_j = {x_p \in \mathcal{T} \ | \ l_p = j, j \in \mathcal{L}}$ defined by its label.
